wind_diagrams

### 2019-12-16 wind_analyses.Rmd
to do
progress

# save(wind_months, file = "Data/wind_months.RData")
```

@@

match_func <- function(df){
  match <- SACTN_US  %>%  
  left_join(df, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}

wind_match <- match_func(df = wind_months) 
```

@@

>>>>

# save(wind_months, file = "Data/wind_m onths.RData")
```

@@

match_func <- function(df){
  match <- df  %>%  
  left_join(wind_months, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}
wind_months <- site_list_sub %>% 
  left_join(wind_months)

wind_match_SACTN <- match_func(df = SACTN_US)

load("Data/OISST.RData") # 2 decimal places
OISST <- BC_avhrr_only_v2_Document_Document

match_func <- function(df){
  match <- df  %>%  
  left_join(wind_months, by = c("lat", "date", "lon")) %>% 
  na.trim()
  return(match)
}
wind_match_OISST <- match_func(df = OISST)

```

@@

Matching the OISST Data and CMC data to match the SACTN dataset

```{r}
unique_pixel <- OISST %>%
  select(lon, lat) %>%
  unique()

# # Select 1 nearest pixel (k = 1)
# # here we ue knnx to find the closes pixel to the insitu sites
match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
                          query = as.matrix(site_list_sub[,5:6]), k = 1)

# # Select SST pixels nearest to insitu sites
pixel_match <- unique_pixel[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>% 
  mutate(site = site_list_sub$site)

combined_OISST_match <- OISST %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)
rm(combined_OISST)

combined_OISST_sites <- combined_OISST_match %>%
  left_join(pixel_match, by = c("combi", "lon", "lat"))

OISST_final <- combined_OISST_sites %>% 
  select(site, date, temp, lat, lon)

############
unique_pixel <- CMC %>%
  select(lon, lat) %>%
  unique()

# # Select 1 nearest pixel (k = 1)
# # here we ue knnx to find the closes pixel to the insitu sites
match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
                          query = as.matrix(site_list_sub[,5:6]), k = 1)

# # Select SST pixels nearest to insitu sites
pixel_match <- unique_pixel[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>% 
  mutate(site = site_list_sub$site)

combined_CMC_match <- CMC %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  filter(combi %in% pixel_match$combi)
# rm(combined_OISST)

combined_CMC_sites <- combined_CMC_match %>%
  left_join(pixel_match, by = c("combi", "lon", "lat"))

CMC_final <- combined_CMC_sites %>% 
  select(site, date, temp, lat, lon) 
```

```{r}

```
